---
title: "Jolinson Richi A"
rollno: '21122030'
output:
  word_document: default
  html_notebook: default
---
 
# Importing the data set (downloaded from kaggle)
```{r}
wine=read.csv("D:\\AJR\\RfrML\\Wine dataset\\winequality-red.csv")
head(wine)
```


# summary function gives the statistical summary of the data it consist of 6 summaries for each variable

```{r}
summary(wine)
```
#str is a fucntion that Compactly display the internal structure of an R object, a diagnostic function and an alternative to summary so in this code 
# its executing the wine data's structure

```{r}
str(wine)
```
#table uses the cross-classifying factors to build a contingency table of the counts at each combination of factor levels.

```{r}
a=table(wine$citric.acid)
a
```
#I defined which rows and column has to be shown as per my desired selections
```{r}
p=wine[c(5:15),c(1:5)]
p
```
# Get or set the length of vectors (including lists) and factors, and of any other R object for which a method has been defined.
```{r}
length(wine)
```
#Returns the first or last parts of a vector, matrix, table, data frame or function. 
```{r}
head(wine)
```
#Returns the first or last parts of a vector, matrix, table, data frame or function. 
```{r}
tail(wine)
```
#  function density computes kernel density estimates. Its default method does so with the given kernel and bandwidth for univariate observations.

```{r}
j=wine$density
print(j)
```
# max functions displays the maximum value occured in a dataset
```{r}
max(wine$quality)
```
# min functions displays the minimum value occured in a dataset
```{r}
min(wine$quality)

```
# mean displayes the mean value of desired column or row

```{r}
mean(wine$pH)
```
# dim funtions shows how many rows and columns are in my dataset
```{r}
dim(wine)
```
# I again showed the mean value of wine quality as a part of my exploration
```{r}
mean(wine$quality)
```
#sd funtions tells the standard deviation
```{r}
sd(wine$quality)

```
#he generic function hist computes a histogram of the given data values.
```{r}
hist(wine$total.sulfur.dioxide,col = "Blue",border = "red")
```
# Produce box-and-whisker plot(s) of the given (grouped) values.
```{r}
boxplot(wine[,0:7],main ='contents in wine',col = "green")
```
# Creates a bar plot with vertical or horizontal bars.
```{r}
wine = head(wine,n=20)
barplot(wine$total.sulfur.dioxide,wine$free.sulfur.dioxide,xlab = "Total Sulfur dioxide",ylab = "Free Sulphur dioxide",col ="red")
```
#free sulfur dioxide means The amount of free SO2 needed is based on the pH of the wine

# it showing the ph level of wine according to my dataset 
```{r}
pie(table(wine$pH),border = "Brown")
```
```{r}
library(ISLR)
attach (wine)
pairs(wine)
```

```{r}
head(wine)
```
```{r}
cor(wine[,c(1:7)])
```



