---
title: "ENDSEM 21122030"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---


```{r}
df=read.csv("C:\\Users\\jolin\\OneDrive\\Desktop\\q3_CarPrice_Assignment - Copy.csv")
```
#read the dataset 

```{r}
head(df)
```
#viewing first 5 rows in the dataset 

```{r}
summary(df)
```

#Finding the total sum of null values present in the dataset, fortunately in this dataset we dont have any null values 
```{r}
sum(is.na(df))
```

#summary of the dataset 

```{r}
str(df)
```
```{r}
library("ggplot2")
gg=ggplot(df,aes(x=horsepower,y=compressionratio))+geom_point(aes(col= peakrpm))+geom_smooth(method="loess",se=F)+labs(subtitle = "HORSPOWER AFFECTING RPM",y="compressionratio",x="horsepower",title="Scatterplot",caption = "Source: POWER")
plot(gg)
```
#In this scaterplot we can clearly see that some of the data has been pointed out the outliers has been found 

```{r}
library("ggplot2")
gg=ggplot(df,aes(x=citympg ,y=highwaympg))+geom_point(aes(col= horsepower))+geom_smooth(method="loess",se=F)+labs(subtitle = "Milege",y="highwaympg",x="citympgr",title="Scatterplot",caption = "Source: POWER")
plot(gg)
```


```{r}
g<-ggplot(df,aes(horsepower,compressionratio,na.rm=TRUE)) 
g+ geom_boxplot(varwidth = T,fill="plum")+
  labs(subtitle="Horsepowe and Combustion capacity",y="compression ratio",x="Horsepower",title="boxplot",caption="Source:Carpredictins")
```
```{r}
g<-ggplot(df,aes(peakrpm ,citympg ,na.rm=TRUE)) 
g+ geom_boxplot(varwidth = T)+
  labs(subtitle="Horsepowe and Combustion capacity",y="citympg ",x="peakrpmr",title="boxplot",caption="Source:Carpredictins")
```

```{r}
str(df)
```



#In this boxplot we can clearly see that some of the data has been pointed out the outliers below and above the boxplot.  

```{r}
library("psych")
describe(df)
```
#measured correlation of the two numeric columns in the dataset

```{r}
a=cor(df[,21:23])
print(a)
```

```{r}
library(corrplot)
corrplot(a)
```

```{r}
Model=lm(carwidth  ~ carheight,horsepower,data =df)
summary(Model)
```

```{r}
plot(Model)
```
```{r}
Model1=lm(curbweight ~ stroke,boreratio,data =df)
summary(Model1)
```
```{r}
plot(Model1)
```
#Training and testing the data 

```{r}
library(caTools)
set.seed(123)
#Split ratio is 75:25
split = sample.split(df$wheelbase, SplitRatio = 0.75)
training_set = subset(df, split == TRUE)
test_set = subset(df, split == FALSE)
```


#Decision tree 

```{r}
library(party)
tree1=ctree(wheelbase ~carlength +carwidth +enginesize+boreratio +stroke+compressionratio+horsepower +peakrpm,data=df) #~target variable,predicting 
tree1
```
```{r}
library(rpart)
mytree=rpart(wheelbase~.,data=df,method = "anova")
mytree
```

```{r}
library(rattle)
library(RColorBrewer)
fancyRpartPlot(mytree,caption=NULL,cex=0.5)
```
```{r}
df=df[-(9)]
```

```{r}
str(df)
```


```{r}
pairs(df)
```
```{r}
library(corrplot)

corrplot(cor(df),
  method = "number",
  type = "upper" )
```

```{r}
s=cor(df)
print(s)
```

```{r}
library(corrplot)
corrplot(s)
```
```{r}
df=df[-(15)]
```

```{r}
str(df)
```
```{r}
q=cor(df)
print(q)
library(corrplot)
corrplot(q)
```


```{r}
# Loading package
library(e1071)
library(caTools)
library(caret)
library(crosstable)
library(gmodels)
```



#Naive bayes

```{r}
index = sample(2,nrow(df),prob = c(0.9,0.1),replace=TRUE) 
set.seed(1234)
train = df[index==1,]
test = df[index==2,]
test_data = test[1:4]
test_label = test[,5]
model=naiveBayes(train$horsepowe~.,train)
model
```
```{r}
test_result=predict(model,test_data)
test_result
```
```{r}
CrossTable(x=test_label, y=test_result)
```